### 2012-04-15 intention motor representation with corrado sinigaglia/conf lyon glasgow was spp submit rejected/intention and motor representation GLASGOW.tex
talk

\def \ititle {Intention and motor representation:}
\def \isubtitle {how to resist temptation}
\def \iauthor {
%S. Butterfill* \& C. Sinigaglia**
%\\ 
%**Department of Philosophy, University of Warwick
%\\ 
%***Dipartimento di Filosofia, Università degli Studi di Milano
}
\def \iemail{
%	s.butterfill@warwick.ac.uk
}
%\date{}

\input{$HOME/Documents/submissions/preamble_steve_paper2}
\author{}
\date{}

@@

\begin{abstract}
\noindent
Are there distinctive roles for intention and motor representation in explaining the purposiveness of action? Standard philosophical accounts of action assign a role to intention but are silent on motor representation. The temptation is to suppose that nothing need be said here because motor representation is either only an enabling condition for purposive action or else merely a variety of intention. Drawing on cognitive and neuroscientific research, this talk identifies reasons for resisting temptation. Some motor representations, like intentions, coordinate actions in virtue of representing outcomes; but, unlike intentions, motor representations cannot feature as premises or conclusions in practical reasoning.  This implies that motor representation has a distinctive role in explaining the purposiveness of action. It also gives rise to a problem: were the roles of intention and motor representation entirely independent, this would impair effective action. Resisting temptation therefore requires explaining how intentions interlock with motor representations. The solution, we argue, is to recognise that the contents of intention can be partially determined by the contents of motor representations. Understanding this content-determining relation enables better understanding how intention is related to action.

\

\noindent
Word count: 3731 including notes, excluding references

@@

@@

What is the relation between a purposive action and the outcome or outcomes to which it is directed? The standard way of answering this question appeals to intention, a propositional attitude which plays a characteristic role in planning and coordinating action, is linked to practical reasoning and is subject to characteristic norms (\citealp{Bratman:1987xw}).  On the standard view, an action is directed to an outcome in virtue of the action's being appropriately related to an intention which represents this outcome or some related outcome. As this view is usually expounded, the relation between actions and outcomes to which they are directed is treated as largely independent of the motor processes and representations underpinning action execution. Motor representations are usually considered either as philosophically irrelevant enabling conditions, or else as merely filling in additional details of the basic schema provided by the standard story. Our aim is to show that this is a mistake:
the standard view must be  refined and extended  to accommodate distinctive roles for intention and motor representation in explaining the purposiveness of action.

>>>>

\def \ititle {Intention and motor representation in purposive action}
\def \isubtitle {}
\def \iauthor {
S. Butterfill* \& C. Sinigaglia**
\\ 
**Department of Philosophy, University of Warwick
\\ 
***Dipartimento di Filosofia, Università degli Studi di Milano
}
\def \iemail{
	s.butterfill@warwick.ac.uk
}

\input{$HOME/Documents/submissions/preamble_steve_paper2}

@@

\begin{abstract}
\noindent
Are there distinct roles for intention and motor representation in explaining the purposiveness of action? Standard accounts of action assign a role to intention but are silent on motor representation. The temptation is to suppose that nothing need be said here because motor representation is either only an enabling condition for purposive action or else merely a variety of intention. This paper provides reasons for resisting that temptation. Some motor representations, like intentions, coordinate actions in virtue of representing outcomes; but, unlike intentions, motor representations cannot feature as premises or conclusions in practical reasoning.  This implies that motor representation has a distinctive role in explaining the purposiveness of action. It also gives rise to a problem: were the roles of intention and motor representation entirely independent, this would impair effective action. It is therefore necessary to explain how intentions interlock with motor representations. The solution, we argue, is to recognise that the contents of intentions can be partially determined by the contents of motor representations. Understanding this content-determining relation enables better understanding how intentions relate to actions.

@@

\section{Pre-Introduction}

Which events are actions?

In philosophy this question is sometimes answered in terms of intention.
For an event to be an action is for it to stand in a special relation to an intention.
This view says nothing at all about how intentions could result in bodily movements; that is considered to be merely a matter of implementation.

In psychology the question is sometimes answered in terms of motor representation.
For an event to be an action is for it to stand in a special relation to a motor representation.
This view says little about actions whose purposes involve things the motor system doesn’t care about---for example, your motor system doesn’t care whether you’re ripping up a real Armani shirt or a fake Armani one, but this sort of difference can affect whether your actions succeed or fail.

You might just say that the two disciplines are talking past each other.
But we want to argue that these two pictures are aspects of a larger theory of action.

@@

A basic question about action is,
What is the relation between a purposive action and the outcome or outcomes to which it is directed? The standard way of answering this question appeals to intention, a propositional attitude which plays a characteristic role in planning and coordinating action, is linked to practical reasoning and is subject to characteristic norms (\citealp{Bratman:1987xw}).  On the standard view, an action is directed to an outcome in virtue of the action's being appropriately related to an intention which represents this outcome or some related outcome. As this view is usually expounded, the relation between actions and outcomes to which they are directed is treated as largely independent of the motor processes and representations underpinning action execution. Motor representations are usually considered either as philosophically irrelevant enabling conditions, or else as merely filling in additional details of the basic schema provided by the standard story. Our aim is to show that this is a mistake:
the standard view must be  refined and extended  to accommodate distinctive roles for intention and motor representation in explaining the purposiveness of action.
